Path Model Temperature Comparisons

### 2016-08-15 path-temp-compare.Rmd
Revise models and examine for spatial autocorrelation.

```{r load data, echo=F}
load("climate-path-model-data.RData")
library(piecewiseSEM)# version 1.1.1, tried most recent version & kept getting errror 7/18/2016 b/c matrices rows were unequal in sem.missing.paths function
library(dplyr)
library(lme4)
library(lmerTest)

@@

## static variables
oakplots.sub$candens15m.scl <- as.numeric(scale(oakplots.sub$candens15m))
oakplots.sub$shannons2005.scl <- as.numeric(scale(oakplots.sub$H.2005))
oakplots.sub$shannons2014.scl <- as.numeric(scale(oakplots.sub$H.2014))
oakplots.sub$twi15m.scl <- as.numeric(scale(oakplots.sub$twi15m))
oakplots.sub$twi15m.log.scl <- as.numeric(scale(oakplots.sub$twi15m.log))
```

@@

Path model with the continuous variables standardized using the default settings of the `scale` function, resulting in each having a mean of zero and standard deviation of one. Each variable is first  centered by subtracting its mean and then scaled by dividing by its standard deviation.
```{r hours >25 path model all oak plots scaled}
model_list1.scl <- list(
      shannons <- lm(shannons2005.scl ~ twi15m.log.scl, data = oakplots.sub),

@@

```{r hours >25 path model all oak plots unscaled, echo=F}
model_list1 <- list(
      shannons <- lm(H.2005 ~ twi15m.log, data = oakplots.sub),

      umca_density <- lmer(tot_bay.log ~ twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

      slc <- lmer(tot_lfct.log ~ tot_bay.log + hrs_abv25ds + avg_hrs1422_wet_t_t1.log + H.2005 + twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

Examining the residual plots of each piece of the path model
```{r shannons residuals plot}
par(mfrow=c(2,2))
plot(shannons, main = "OLS regression of diversity ~ wetness index residuals")
par(mfrow=c(1,1))
plot(shannons$model$twi15m.log, resid(shannons),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Diversity model residuals vs. wetness index predictor")
```

```{r bay laurel density residuals plot}
plot(umca_density, main = "LMM of bay laurel density residuals")
plot(umca_density@frame$twi15m.log, resid(umca_density),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Bay laurel density model residuals vs. wetness index predictor")
```

```{r symptomatic leaf count residuals plot}
plot(slc, main = "LMM of symptomatic leaf count residuals")
plot(slc@frame$umca_density_ha.log, resid(slc),
     xlab = "bay laurel density",
     ylab = "model residuals",
     main = "SLC model residuals vs. bay laurel density predictor")
plot(slc@frame$hrs_abv25ds, resid(slc),
     xlab = "# dry-season hours >25 C",
     ylab = "model residuals",
     main = "SLC model residuals vs. dry-season hours >25 C predictor")
plot(slc@frame$avg_hrs1422_wet_t_t1.log,
     xlab = "avg. wet-hours 14-22C",
     ylab = "model residuals",
     main = "SLC model residuals vs. wet-hours predictor")
plot(slc@frame$H.2005, resid(slc),
     xlab = "Shannon's diversity index",
     ylab = "model residuals",
     main = "SLC model residuals vs. Shannon's diversity predictor")
plot(slc@frame$twi15m.log, resid(slc),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "SLC model residuals vs. wetness index predictor")
```

```{r wet-hours residuals plot}
plot(wet_hours_1422, main = "LMM of avg. # of hours 14-22 C current & prev. year residuals")
plot(wet_hours_1422@frame$umca_density_ha.log, resid(wet_hours_1422),
     xlab = "bay laurel density",
     ylab = "model residuals",
     main = "Wet-hours model residuals vs. bay laurel density predictor")
```

```{r dry-season hours residuals plot}
plot(hrs_abv25, main = "LMM of # of hours >25 C during prev. dry season residuals")
plot(hrs_abv25@frame$twi15m.log, resid(hrs_abv25),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Dry-season hours model residuals vs. wetness index predictor")
```

```{r oak infection residuals plot}
plot(oak_infection, main = "Binomial GLMM of oak infection residuals")
plot(oak_infection@frame$tot_lfct.log, resid(oak_infection),
     xlab = "symptomatic leaf count",
     ylab = "model residuals",
     main = "Oak infection model residuals vs. symptomatic leaf count predictor")
plot(oak_infection@frame$avg_hrs1422_wet_t_t1.log, resid(oak_infection),
     xlab = "avg. wet-hours 14-22C",
     ylab = "model residuals",
     main = "Oak infectin model residuals vs. wet-hours predictor")
plot(oak_infection@frame$H.2005, resid(oak_infection),
     xlab = "Shannon's diversity index",
     ylab = "model residuals",
     main = "Oak infection model residuals vs. diversity predictor")
```

@@

```{r fit and compare all oak plots vs >0 bay laurel oak plots}
# Comparing fits of the piecewise models using all oak plots vs. plots with oaks and at least one bay laurel
sem.fit(model_list1, oakplots.sub, 
        corr.errors = c("hrs_abv25ds ~~ avg_hrs1422_wet_t_t1.log"))
sem.fit(model_list1.scl, oakplots.sub,
          corr.errors = c("hrs_abv25ds.scl ~~ avg_hrs1422_wet_t_t1.log.scl"))

>>>>

```{r load data, echo=F}
load("climate_path_model_data.RData")
library(piecewiseSEM)# version 1.1.1, tried most recent version & kept getting errror 7/18/2016 b/c matrices rows were unequal in sem.missing.paths function
library(dplyr)
library(lme4)
library(lmerTest)

@@

## static variables
oakplots.sub$candens15m.scl <- as.numeric(scale(oakplots.sub$candens15m))
oakplots.sub$shannons2005.scl <- as.numeric(scale(oakplots.sub$H.2005))
oakplots.sub$shannons2014.scl <- as.numeric(scale(oakplots.sub$H.2014))
oakplots.sub$twi15m.scl <- as.numeric(scale(oakplots.sub$twi15m))
oakplots.sub$twi15m.log.scl <- as.numeric(scale(oakplots.sub$twi15m.log))

plot_coords <- select(plots_shp@data, PLOT_ID, X, Y)
plot_coords$PLOT_ID <- tolower(plot_coords$PLOT_ID)
oakplots.sub <- left_join(oakplots.sub, plot_coords, by = c("plotid"="PLOT_ID"))
oakplots.2006 <- left_join(oakplots.2006, plot_coords, by = c("plotid"="PLOT_ID"))

oakplots.2006$twi15m.log.scl <- as.numeric(scale(oakplots.2006$twi15m.log))
oakplots.2006$shannons2005.scl <- as.numeric(scale(oakplots.2006$H.2005))

## convert grouping variables to factors
oakplots.sub$plotid <- as.factor(oakplots.sub$plotid)
oakplots.sub$sample_year <- as.factor(oakplots.sub$sample_year)
```

@@

Path model with the continuous variables standardized using the default settings of the `scale` function, resulting in each having a mean of zero and standard deviation of one. Each variable is first  centered by subtracting its mean and then scaled by dividing by its standard deviation.
```{r hours >25 path model all oak plots scaled}
model_list1.scl <- list(
      shannons <- lm(shannons2005.scl ~ twi15m.log.scl, data = oakplots.2006),

@@

```{r hours >25 path model all oak plots unscaled, echo=F}
model_list1 <- list(
      shannons <- lm(H.2005 ~ twi15m.log, data = oakplots.2006),

      umca_density <- lmer(umca_density_ha.log.scl ~ twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

      slc <- lmer(tot_lfct.log ~ umca_density_ha.log.scl + hrs_abv25ds + avg_hrs1422_wet_t_t1.log + H.2005 + twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

      wet_hours_1422 <- lmer(avg_hrs1422_wet_t_t1.log ~ umca_density_ha.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

Examining the residual plots of each piece of the path model and checking for spatial autocorrelation in the residuals.
```{r general code for testing SAC, echo=F, eval=F}
### Check for spatial autocorrelation in residuals

#install.packages('ape')
library(ape)

### Create inverse distance matrix
points <- as.matrix(dist(cbind(data$x, data$y)))
points.inv <- 1/points
diag(points.inv) <- 0
# points.inv [is.infinite(points.inv)]<-0 
# WAS GETTING ERROR - if (obs <= ei) 2 * pv else 2 * (1 - pv) : 
# missing value where TRUE/FALSE needed, this fixed the infinite values in the data

### Calculate Moran's I
Moran.I(model.residuals, points.inv) 
### Additional description calculating Moran's I in R: http://www.ats.ucla.edu/stat/r/faq/morans_i.htm
### Where model.residuals = residuals(model)
```

```{r shannons residuals plot, echo=F}
par(mfrow=c(2,2))
plot(shannons, main = "OLS regression of diversity ~ wetness index residuals")
par(mfrow=c(1,1))
plot(shannons$model$twi15m.log, resid(shannons),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Diversity model residuals vs. wetness index predictor")
```

```{r test SAC diversity model residuals, echo=F}
library(spBayes); library(classInt); library(RColorBrewer); library(geoR)
summary(na.omit(oakplots.2006))
points <- select(na.omit(oakplots.2006), X, Y)
points <- as.matrix(dist(cbind(points$X, points$Y)))
points.inv <- 1/points
diag(points.inv) <- 0
shannons.resids <- resid(shannons)
max.dist <- 0.33 * max(iDist(points))
bins <- 100

vario.shannons <- variog(coords = points, 
                     data = na.omit(oakplots.2006$shannons2005.scl),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.shannons <- variofit(
      vario.shannons,
      ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.shannons)
lines(fit.vario.shannons)
abline(h = fit.vario.shannons$nugget, col = "blue")# nugget
abline(h = fit.vario.shannons$cov.pars[1] + fit.vario.shannons$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.shannons$cov.pars[2], col = "red3")# range

vario.shannons.resid <- variog(coords = points,
                               data = shannons.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.shannons.resid <- variofit(
      vario.shannons.resid,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.shannons.resid)
lines(fit.vario.shannons.resid)
abline(h = fit.vario.shannons.resid$nugget, col = "blue")# nugget
abline(h = fit.vario.shannons.resid$cov.pars[1] + fit.vario.shannons.resid$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.shannons.resid$cov.pars[2], col = "red3")# range

Moran.I(shannons.resids, points.inv)
# Significant p-value, but no pattern in the model residuals 
```

```{r bay laurel density residuals plot, echo=F}
plot(umca_density, main = "LMM of bay laurel density residuals")
plot(umca_density@frame$twi15m.log, resid(umca_density),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Bay laurel density model residuals vs. wetness index predictor")
```

```{r test SAC bay density model, echo=F}
# Test SAC of residuals
umca_density.resids <- resid(umca_density)
plots1 <- select(umca_density@frame, plotid)
plots1 <- as.vector(plots1$plotid)
plots1 <- as.data.frame(plots1)
names(plots1) <- "plotid"
# plots1$plotid <- as.character(plots1$plotid)
str(plots1)

plots2 <- select(plots_shp@data, PLOT_ID, X, Y)
# plots2$plotid <- as.character(plots2$plotid)
names(plots2) <- tolower(names(plots2))
plots2$plot_id <- tolower(plots2$plot_id)
str(plots2)

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario.umca_density <- variog(coords = points_rep, 
                     data = na.omit(umca_density@frame$tot_bay.log),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density <- variofit(
      vario.umca_density,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.umca_density)
lines(fit.vario.umca_density)
abline(h = fit.vario.umca_density$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density$cov.pars[1] + fit.vario.umca_density$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density$cov.pars[2], col = "red3")# range

vario.umca_density.resids <- variog(coords = points_rep,
                               data = umca_density.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density.resids <- variofit(
      vario.umca_density.resids,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
# par(mfrow = c(1,2))
plot(vario.umca_density.resids)
lines(fit.vario.umca_density.resids)
abline(h = fit.vario.umca_density.resids$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density.resids$cov.pars[1] + fit.vario.umca_density.resids$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density.resids$cov.pars[2], col = "red3")# range

Moran.I(umca_density.resids, points_rep.inv)

# length(umca_density.resids)
# dim(points_rep)
```

```{r symptomatic leaf count residuals plot, echo=F}
plot(slc, main = "LMM of symptomatic leaf count residuals")
plot(slc@frame$umca_density_ha.log, resid(slc),
     xlab = "bay laurel density",
     ylab = "model residuals",
     main = "SLC model residuals vs. bay laurel density predictor")
plot(slc@frame$hrs_abv25ds, resid(slc),
     xlab = "# dry-season hours >25 C",
     ylab = "model residuals",
     main = "SLC model residuals vs. dry-season hours >25 C predictor")
plot(slc@frame$avg_hrs1422_wet_t_t1.log,
     xlab = "avg. wet-hours 14-22C",
     ylab = "model residuals",
     main = "SLC model residuals vs. wet-hours predictor")
plot(slc@frame$H.2005, resid(slc),
     xlab = "Shannon's diversity index",
     ylab = "model residuals",
     main = "SLC model residuals vs. Shannon's diversity predictor")
plot(slc@frame$twi15m.log, resid(slc),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "SLC model residuals vs. wetness index predictor")
```

```{r test SAC of slc model residuals, echo=F}
# Test SAC of residuals
slc.resids <- resid(slc)
plots1 <- select(slc@frame, plotid)
plots1 <- as.vector(plots1$plotid)
plots1 <- as.data.frame(plots1)
names(plots1) <- "plotid"
# plots1$plotid <- as.character(plots1$plotid)
str(plots1)

plots2 <- select(plots_shp@data, PLOT_ID, X, Y)
# plots2$plotid <- as.character(plots2$plotid)
names(plots2) <- tolower(names(plots2))
plots2$plot_id <- tolower(plots2$plot_id)
str(plots2)

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario.slc <- variog(coords = points_rep, 
                     data = na.omit(slc@frame$tot_lfct.log),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.slc <- variofit(
      vario.slc,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.slc)
lines(fit.vario.slc)
abline(h = fit.vario.slc$nugget, col = "blue")# nugget
abline(h = fit.vario.slc$cov.pars[1] + fit.vario.slc$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.slc$cov.pars[2], col = "red3")# range

vario.slc.resids <- variog(coords = points_rep,
                               data = slc.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.slc.resids <- variofit(
      vario.slc.resids,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
# par(mfrow = c(1,2))
plot(vario.slc.resids)
lines(fit.vario.slc.resids)
abline(h = fit.vario.slc.resids$nugget, col = "blue")# nugget
abline(h = fit.vario.slc.resids$cov.pars[1] + fit.vario.slc.resids$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.slc.resids$cov.pars[2], col = "red3")# range

Moran.I(slc.resids, points_rep.inv)
```

```{r wet-hours residuals plot, echo=F}
plot(wet_hours_1422, main = "LMM of avg. # of hours 14-22 C current & prev. year residuals")
plot(wet_hours_1422@frame$umca_density_ha.log, resid(wet_hours_1422),
     xlab = "bay laurel density",
     ylab = "model residuals",
     main = "Wet-hours model residuals vs. bay laurel density predictor")
```

```{r test SAC wet-hours residuals, echo=F}
# Test SAC of residuals
wet_hours.resids <- resid(wet_hours_1422)
plots1 <- select(wet_hours_1422@frame, plotid)
plots1 <- as.vector(plots1$plotid)
plots1 <- as.data.frame(plots1)
names(plots1) <- "plotid"
# plots1$plotid <- as.character(plots1$plotid)
str(plots1)

plots2 <- select(plots_shp@data, PLOT_ID, X, Y)
# plots2$plotid <- as.character(plots2$plotid)
names(plots2) <- tolower(names(plots2))
plots2$plot_id <- tolower(plots2$plot_id)
str(plots2)

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario. <- variog(coords = points_rep, 
                     data = na.omit(umca_density@frame$tot_bay.log),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density <- variofit(
      vario.umca_density,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.umca_density)
lines(fit.vario.umca_density)
abline(h = fit.vario.umca_density$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density$cov.pars[1] + fit.vario.umca_density$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density$cov.pars[2], col = "red3")# range

vario.umca_density.resids <- variog(coords = points_rep,
                               data = umca_density.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density.resids <- variofit(
      vario.umca_density.resids,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
# par(mfrow = c(1,2))
plot(vario.umca_density.resids, 
     main = "Variogram - UMCA deensity model residuals",
     xlab = "distance (m)")
lines(fit.vario.umca_density.resids)
abline(h = fit.vario.umca_density.resids$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density.resids$cov.pars[1] + fit.vario.umca_density.resids$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density.resids$cov.pars[2], col = "red3")# range

Moran.I(wet_hours.resids, points_rep.inv)
```

```{r dry-season hours residuals plot, echo=F}
plot(hrs_abv25, main = "LMM of # of hours >25 C during prev. dry season residuals")
plot(hrs_abv25@frame$twi15m.log, resid(hrs_abv25),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Dry-season hours model residuals vs. wetness index predictor")
```

```{r test SAC dry-season model residuals, echo=F}
# Test SAC of residuals
hrs_abv25.resids <- resid(hrs_abv25)
plots1 <- select(hrs_abv25@frame, plotid)
plots1 <- as.vector(plots1$plotid)
plots1 <- as.data.frame(plots1)
names(plots1) <- "plotid"
# plots1$plotid <- as.character(plots1$plotid)
str(plots1)

plots2 <- select(plots_shp@data, PLOT_ID, X, Y)
# plots2$plotid <- as.character(plots2$plotid)
names(plots2) <- tolower(names(plots2))
plots2$plot_id <- tolower(plots2$plot_id)
str(plots2)

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

Moran.I(hrs_abv25.resids, points_rep.inv)
```

```{r oak infection residuals plot, echo=F}
plot(oak_infection, main = "Binomial GLMM of oak infection residuals")
plot(oak_infection@frame$tot_lfct.log, resid(oak_infection),
     xlab = "symptomatic leaf count",
     ylab = "model residuals",
     main = "Oak infection model residuals vs. symptomatic leaf count predictor")
plot(oak_infection@frame$avg_hrs1422_wet_t_t1.log, resid(oak_infection),
     xlab = "avg. wet-hours 14-22C",
     ylab = "model residuals",
     main = "Oak infectin model residuals vs. wet-hours predictor")
plot(oak_infection@frame$H.2005, resid(oak_infection),
     xlab = "Shannon's diversity index",
     ylab = "model residuals",
     main = "Oak infection model residuals vs. diversity predictor")
```

```{r test SAC of oak infection residuals, echo=F}
# Test SAC of residuals
oak_infection.resids <- resid(oak_infection)
plots1 <- select(oak_infection@frame, plotid)
plots1 <- as.vector(plots1$plotid)
plots1 <- as.data.frame(plots1)
names(plots1) <- "plotid"
# plots1$plotid <- as.character(plots1$plotid)
str(plots1)

plots2 <- select(plots_shp@data, PLOT_ID, X, Y)
# plots2$plotid <- as.character(plots2$plotid)
names(plots2) <- tolower(names(plots2))
plots2$plot_id <- tolower(plots2$plot_id)
str(plots2)

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

Moran.I(oak_infection.resids, points_rep.inv)
```

@@

```{r fit and compare all oak plots vs >0 bay laurel oak plots}
# Comparing fits of the piecewise models using all oak plots vs. plots with oaks and at least one bay laurel
(sem.fit(model_list1, oakplots.sub, 
        corr.errors = c("hrs_abv25ds ~~ avg_hrs1422_wet_t_t1.log")))
(sem.fit(model_list1.scl, oakplots.sub,
          corr.errors = c("hrs_abv25ds.scl ~~ avg_hrs1422_wet_t_t1.log.scl")))
